4d $\cN=1$

### 2019-11-14 6dsusy.tex
6d

@@

Next, we collect all terms in Equation (\ref{CMEhyper3}) proportional to $\psi^*$:
\begin{align*}
& - \frac{1}{2} \rho(\d(Q_1,\psi))Q_2 - \frac{1}{2} \rho(\d(Q_2, \psi)) Q_1 - \Gamma(Q_1,Q_2) . \psi
\\ 
& + \frac{1}{2} \rho(\Gamma(Q_1,Q_2)) \sd \dd \psi \textcolor{red}{ - \frac{1}{2} (Q_2, \sd \dd \psi)Q_1 - \frac{1}{2} (Q_1, \sd \dd \psi)Q_2}
\end{align*}
By Proposition \ref{prop:cliffordactionproperties} item (2), the first, second, and fourth terms combine to give
\[
- \frac{1}{2} \left( \sd \dd \rho(\Gamma(Q,\psi)) Q_2 + \sd \dd \rho(\Gamma(Q_2, \psi))Q_1 \right)  .
\]
This term is equal to $\frac{1}{2} \sd \dd \rho(\Gamma(Q_1,Q_2)) \psi$ by \ref{prop:3psi}. 
The Clifford relation implies this term cancels with the remaining terms.

\end{proof}

>>>>

\brian{This holds for $\Sigma = S_+ \otimes W_+$.}

\begin{prop}\label{prop: new3psi}
Suppose $Q_1,Q_2 \in \Sigma = S_+ \otimes W_+$ and $Q_3 \in S_-$. 
Then
\[
(Q_1, Q_3) Q_2 + (Q_2, Q_3)Q_1 = \rho(\Gamma(Q_1,Q_2)) Q_3
\]
\end{prop}

@@

Next, we collect all terms in Equation (\ref{CMEhyper3}) proportional to $\psi^*$:
\begin{equation}\label{psistar}
\begin{array}{cccc}
& - & \displaystyle \frac{1}{2} \rho(\d(Q_1,\psi))Q_2 - \frac{1}{2} \rho(\d(Q_2, \psi)) Q_1 - \Gamma(Q_1,Q_2) . \psi
\\ 
& + &\displaystyle \frac{1}{2} \rho(\Gamma(Q_1,Q_2)) \sd \dd \psi \textcolor{red}{ - \frac{1}{2} (Q_2, \sd \dd \psi)Q_1 - \frac{1}{2} (Q_1, \sd \dd \psi)Q_2}
\end{array}
\end{equation}
By Proposition \ref{prop:cliffordactionproperties} item (3), the first and second terms can be written as:
\[
- \frac{1}{2} \rho(\d(Q_1,\psi))Q_2 - \frac{1}{2} \rho(\d(Q_2, \psi)) Q_1 = - \frac{1}{2} \sd \dd \left( (Q_1, \psi)Q_2 + (Q_2 , \psi)Q_1 \right).
\]
Applying Proposition \ref{prop: new3psi}, to $Q_3 = \psi$, this becomes $-\frac{1}{2} \sd \dd \rho(\Gamma(Q_1,Q_2) \psi)$. 
Finally, by the Clifford identity, the sum of this term with the fourth term in (\ref{psistar}) is precisely $\Gamma(Q_1,Q_2) . \psi$.
So the expression (\ref{psistar}) is identically zero. 
\end{proof}
